Meta-analysis

### 2019-11-01 02_Weather.Rmd
Changed data import corrected some code from changed data files

@@

# Import dataset
PM.dat <-
   read_csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
PM.dat <- PM.dat %>%
   mutate(trial_ref = as.factor(trial_ref)) %>%
   mutate(location = as.factor(location)) %>%
   mutate(host_genotype = as.factor(host_genotype)) %>%
   mutate(fungicide_ai = as.factor(fungicide_ai)) %>%
   mutate(trade_name = as.factor(trade_name)) %>%
   mutate(year = as.factor(year)) %>%
   mutate(replicates = as.factor(replicates)) %>%
   mutate(planting_date = as.Date(planting_date, format = "%d/%m/%Y")) %>%
   mutate(emergence_date = as.Date(emergence_date, format = "%d/%m/%Y")) %>%
   mutate(flowering_date = as.Date(flowering_date, format = "%d/%m/%Y")) %>%
   mutate(pod_final_date = as.Date(pod_final_date, format = "%d/%m/%Y")) %>%
   mutate(mid_late_pod_final = as.Date(mid_late_pod_final, format = "%d/%m/%Y")) %>%
   mutate(first_sign_disease = as.Date(first_sign_disease, format = "%d/%m/%Y")) %>%
   mutate(fungicide_application_1 = as.Date(fungicide_application_1, format = "%d/%m/%Y")) %>%
   mutate(fungicide_application_2 = as.Date(fungicide_application_2, format = "%d/%m/%Y")) %>%
   mutate(fungicide_application_3 = as.Date(fungicide_application_3, format = "%d/%m/%Y")) %>%
   mutate(fungicide_application_4 = as.Date(fungicide_application_4, format = "%d/%m/%Y")) %>%
   mutate(fungicide_application_5 = as.Date(fungicide_application_5, format = "%d/%m/%Y")) %>%
   mutate(fungicide_application_6 = as.Date(fungicide_application_6, format = "%d/%m/%Y")) %>%
   mutate(fungicide_application_7 = as.Date(fungicide_application_7, format = "%d/%m/%Y")) %>%
   mutate(harvest_date = as.Date(harvest_date, format = "%d/%m/%Y")) %>%
   mutate(final_assessment = as.Date(final_assessment, format = "%d/%m/%Y"))

@@

# silo.API <- "YeTZsWlFNC8hvbQLllv8KtbRQWsje4qxic5QQ7mL"
# # retrieve the maximum temperatures from the six yearsd between 2011 and 2017 at weather station 041525 (Hermitage)
# silo_war_Tmax <- getPPD2(station_id = 041525,start = 20110101,end = 20160630, silo.apikey = silo.API, variables = "max_temp,min_temp,daily_rain")
# # retrieve the maximum temperatures from the six yearsd between 2011 and 2017 by location
# silo_king_Tmax <- getPPD2(lat = -26.58, long = 151.83, start = 20110101, end = 20160630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
# silo_gatton_Tmax <- getPPD2(lat = -27.56, long = 152.32, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
# silo_emerald_Tmax <- getPPD2(lat = -23.54, long = 148.19, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")

@@

# Add columns for Year and date to data
king_Tm_aver <- king_Tm_aver %>%
   mutate(
      Year = substr(king_Tm_aver$date, start = 1, stop = 4),
      Day = ymd(king_Tm_aver$date)
   )

# Create data subset of powdery mildew data means for the first sign of the disease by location
King_FS <- PM.dat %>%
   group_by(trial_ref, location, year) %>%
   summarise(first_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
   filter(location == "Kingaroy") %>%
   mutate(day = ymd(first_sign))
str(king_Tm_aver)
str(King_FS)
ggplot(subset(king_Tm_aver, year == levels(factor(King_FS$year))),
       aes(day)) +
   geom_line(aes(y = max_T, colour = year)) +
   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
   geom_line(aes(y = min_T, colour = Year)) +
   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
        title = "Maximum and minimum daily temperatures in Kingaroy") +
   scale_y_continuous(limits = c(0, 40)) +
   scale_x_continuous(
      limits = c(0, 200),
      labels = c(subset(king_Tm_aver, Year == 2016)$date[c(1, 50, 100, 150, 200)]),
      breaks = c(1, 50, 100, 150, 200)
   ) +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   geom_vline(
      xintercept = King_FS$day[1],
      size = 1,
      colour = cols1[1],
      linetype = "dotted"
   ) +
   geom_vline(
      xintercept = King_FS$day[2],
      size = 1.5,
      colour = cols1[2],
      linetype = "dotted"
   ) +
   geom_vline(
      xintercept = King_FS$Day[3],
      size = 1,
      colour = cols1[3],
      linetype = "dashed"
   ) +
   geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5) +
   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))
#   scale_x_continuous(limits = c(1,180),
#                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
#                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
```

>>>>

```{r import_libraries_&_data}
source("R/import_data.R")
PM.dat <- import_data()  # importing means yield and disease severity for each treatment within each powdery mildew trial on mungbean
source("R/year2day.r")

@@

# Import dataset

@@

@@

# Add columns for Year and date to data
king_Tm_aver <- king_Tm_aver %>%
   mutate(
      Year = substr(king_Tm_aver$date, start = 1, stop = 4),
      Day = year2day(king_Tm_aver$date)
   )

# Create data subset of powdery mildew data means for the first sign of the disease by location
King_FS <- PM.dat %>%
   group_by(trial_ref, location, year) %>%
   summarise(first_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
   filter(location == "Kingaroy") %>%
   mutate(day = year2day(first_sign))

ggplot(subset(king_Tm_aver, year == levels(factor(King_FS$year))),
       aes(day)) +
   geom_line(aes(y = max_T, colour = year)) +
   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
   geom_line(aes(y = min_T, colour = Year)) +
   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
        title = "Maximum and minimum daily temperatures in Kingaroy") +
   scale_y_continuous(limits = c(0, 40)) +
   scale_x_continuous(
      limits = c(0, 200),
      labels = c(subset(king_Tm_aver, Year == 2016)$date[c(1, 50, 100, 150, 200)]),
      breaks = c(1, 50, 100, 150, 200)
   ) +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   geom_vline(
      xintercept = King_FS$day[1],
      size = 1,
      colour = cols1[1],
      linetype = "dotted"
   ) +
   geom_vline(
      xintercept = King_FS$day[2],
      size = 1.5,
      colour = cols1[2],
      linetype = "dotted"
   ) +
   geom_vline(
      xintercept = King_FS$Day[3],
      size = 1,
      colour = cols1[3],
      linetype = "dashed"
   ) +
   geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5) +
   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))
#   scale_x_continuous(limits = c(1,180),
#                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
#                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
```
